---
title: "Framing effect analysis"
author: "Ashish"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    number_sections: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    theme: paper
---
Initialization
===
```{r, message=FALSE}
rm(list=ls())

library(psych)
library(lmerTest)

library(sjPlot)
library(here)
library(tidyverse)
theme_set(theme_bw())
```

```{r, eval=FALSE}
library(tidylog)
```


Preprocessing
===

Functions
---
```{r}
logit2prob <- function(logit){
  odds <- exp(logit)
  prob <- odds / (1 + odds)
  return(prob)
}
```

Read data
---
```{r, message=FALSE}
filepath <- "data/proc/ds.jeanroisse.alexithymia.csv"
df_raw <- read_csv(here(filepath))
```

Process data
---

Create processed dataframe
```{r}
df_proc <- df_raw %>% 
   # -- remove people who clearly faked age -- #
  mutate(age = ifelse(age > 18, age, NA)) 
```

Create PAQ dataframe
```{r, message=FALSE}
df_paq <- df_proc %>% 
  select(id, starts_with("paq")) %>% 
  pivot_longer(-id) %>% 
  group_by(id) %>% 
  summarize(paq = mean(value))
```

Create framing effect dataframes  

 - 0 = safe
 - 1 = risk
```{r}
df_framing_w <- df_proc %>% 
  select(id, matches("[gl]t$"))

df_framing_l <- df_proc %>% 
  select(id, matches("[gl]t$")) %>% 
  pivot_longer(-id, names_to = "vignette", values_to = "choice") %>% 
  filter(!is.na(choice)) %>% 
  mutate(frame = case_when(
    str_detect(vignette, "gt$") ~ "gain",
    str_detect(vignette, "lt$") ~ "loss"
  )) %>% 
  mutate(gov = case_when(
    str_detect(vignette, "^c_") ~ "county",
    TRUE ~ "municipal"
  )) %>% 
  mutate(vignette = str_replace(vignette, "^c_", "")) %>% 
  # -- keep only municipal politicians -- #
  filter(gov == "municipal")
```

Check number of trials per participant
```{r}
df_framing_l %>% 
  group_by(id) %>% 
  summarize(n = n()) %>% 
  arrange(desc(n))

df_framing_l %>% 
  group_by(id, gov) %>% 
  summarize(n = n()) %>% 
  summarize(n = n()) %>% 
  arrange(desc(n))
    
```


```{r, echo=FALSE}
# ------ End Preprocessing ------ #
# ----- Run all chunks above -----#
```

Reliability
===
```{r}
df_proc %>% 
  select(starts_with("paq")) %>% 
  psych::alpha(.)
```

Distributions
===
```{r}
df_paq$paq %>% qplot(binwidth=.25)
```


H1
===
H1: Participants are risk-seeking in the gain treatment and risk-averse in the loss treatment.
```{r}
fit <- df_framing_l %>% 
  glmer(choice ~ frame + (1|id) + (1|vignette) ,family = "binomial", .)
summary(fit)
coef(fit)$id[["frameloss"]][[1]]  # odds ratio
logit2prob(coef(fit)$id[["frameloss"]][[1]])  # pr of risky in loss frame
```
> Supported

H2 
===
H2: Alexithymia is positively associated with risk-taking behavior (i.e., lower levels of emotional awareness hamper participants’ ability to become emotionally aware of the issues and dilemmas posed by framing, hence making them more inclined to taking risks).

```{r}
fit <- df_framing_l %>% 
  left_join(df_paq) %>% 
  glmer(choice ~ paq + (1|id) + (1|vignette) ,family = "binomial", .)
summary(fit)
exp(coef(fit)$id[["paq"]][[1]])  # odds ratio
logit2prob(coef(fit)$id[["paq"]][[1]])  # pr risky as function of alx

```
> Not supported

H3 
===
H3: Alexithymia is negatively associated with framing effects (i.e., higher levels of emotional awareness make participants more inclined to respond to the framed situations and hence more susceptible to framing effects.
```{r}
fit <- df_framing_l %>% 
  left_join(df_paq) %>% 
  glmer(choice ~ paq*frame + (1|id) + (1|vignette) ,family = "binomial", .)
summary(fit)
plot_model(fit, type = "int")
```
> Marginally signifciant support


Secondary analyses
===

Moderation by domain
```{r}


```



Session Info
===
```{r}
sessionInfo()
```

