---
title: "Framing effect analysis"
author: "Ashish"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    number_sections: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    theme: paper
---
Initialization
===
```{r, message=FALSE}
rm(list=ls())

library(psych)
library(lmerTest)

library(sjPlot)
library(here)
library(tidyverse)
theme_set(theme_bw())
```

```{r, eval=FALSE}
library(tidylog)
```


Preprocessing
===

Functions
---
```{r}
logit2prob <- function(logit){
  odds <- exp(logit)
  prob <- odds / (1 + odds)
  return(prob)
}
```

Read data
---
```{r, message=FALSE}
filepath <- "data/proc/ds.jeanroisse.alexithymia.csv"
df_raw <- read_csv(here(filepath))
```

Process data
---

Create processed dataframe
```{r}
df_proc <- df_raw %>% 
   # -- remove people who clearly faked age -- #
  mutate(age = ifelse(age > 18, age, NA)) %>% 
  # -- factorize -- #
  mutate(gender = as.factor(gender)) %>% 
  # -- make key issues vars -- #
  mutate(keyIssue_digitization = ifelse(Key_issues_Norway == 5, 1, 0)) %>% 
  mutate(keyIssue_econ = ifelse(Key_issues_Norway == 10, 1, 0)) %>% 
  mutate(keyIssue_employ = ifelse(Key_issues_Norway == 11, 1, 0)) 
```

Create individual difference dataframe
```{r, message=FALSE}
df_inddiff <- df_proc %>% 
  select(id, starts_with("paq")) %>% 
  pivot_longer(-id) %>% 
  group_by(id) %>% 
  summarize(paq = mean(value))  %>% 
  # -- re-add indiv diff vars -- #
  left_join(df_proc %>% select(id, age, gender, matches("keyIssue")))
```

Create framing effect dataframes  

 - 0 = safe
 - 1 = risk
```{r}
df_framing_w <- df_proc %>% 
  select(id, matches("[gl]t$"))

df_framing_l <- df_proc %>% 
  select(id, matches("[gl]t$")) %>% 
  pivot_longer(-id, names_to = "vignette", values_to = "choice") %>% 
  filter(!is.na(choice)) %>% 
  mutate(frame = case_when(
    str_detect(vignette, "gt$") ~ "gain",
    str_detect(vignette, "lt$") ~ "loss"
  )) %>% 
  mutate(gov = case_when(
    str_detect(vignette, "^c_") ~ "county",
    TRUE ~ "municipal"
  )) %>% 
  # -- reformat vignette labels -- #
  mutate(vignette = str_replace(vignette, "^c_", "")) %>% 
  mutate(vignette = str_replace(vignette, "[gl]t$", "")) %>% 
  # -- set econ as reference level -- #
  mutate(vignette = relevel(as.factor(vignette), "econ")) %>% 
  # -- keep only municipal politicians -- #
  filter(gov == "municipal") %>% 
  # -- add key issue binary var -- #
  left_join(df_proc %>% select(id, age, gender, matches("keyIssue"))) %>% 
  mutate(keyIssue = case_when(
    vignette == "dp" & keyIssue_digitization == 1 ~ 1,
    vignette == "dpecon" & keyIssue_digitization == 1 ~ 1,
    vignette == "econ" & keyIssue_employ == 1 ~ 1,
    vignette == "dpecon"& keyIssue_employ == 1 ~ 1,
    TRUE ~ 0
  )) %>% 
  select(-matches("keyIssue_"))
```

Check number of trials per participant
```{r}
df_framing_l %>% 
  group_by(id) %>% 
  summarize(n = n()) %>% 
  arrange(desc(n))

df_framing_l %>% 
  group_by(id, gov) %>% 
  summarize(n = n()) %>% 
  summarize(n = n()) %>% 
  arrange(desc(n))
    
```


```{r, echo=FALSE}
# ------ End Preprocessing ------ #
# ----- Run all chunks above -----#
```

Reliability
===
```{r}
df_proc %>% 
  select(starts_with("paq")) %>% 
  psych::alpha(.)
```

Distributions
===
```{r}
df_inddiff$paq %>% qplot(binwidth=.25)
```


H1
===
H1: Participants are risk-seeking in the gain treatment and risk-averse in the loss treatment.
```{r}
fit <- df_framing_l %>% 
  glmer(choice ~ frame + (1|id) + (1|vignette) ,family = "binomial", .)
summary(fit)
coef(fit)$id[["frameloss"]][[1]]  # odds ratio
logit2prob(coef(fit)$id[["frameloss"]][[1]])  # pr of risky in loss frame
```
> Supported

H2 
===
H2: Alexithymia is positively associated with risk-taking behavior (i.e., lower levels of emotional awareness hamper participants’ ability to become emotionally aware of the issues and dilemmas posed by framing, hence making them more inclined to taking risks).

```{r}
fit <- df_framing_l %>% 
  left_join(df_inddiff) %>% 
  glmer(choice ~ paq + (1|id) + (1|vignette) ,family = "binomial", .)
summary(fit)
exp(coef(fit)$id[["paq"]][[1]])  # odds ratio
logit2prob(coef(fit)$id[["paq"]][[1]])  # pr risky as function of alx

```
> Not supported

H3 
===
H3: Alexithymia is negatively associated with framing effects (i.e., higher levels of emotional awareness make participants more inclined to respond to the framed situations and hence more susceptible to framing effects.
```{r}
fit <- df_framing_l %>% 
  left_join(df_inddiff) %>% 
  glmer(choice ~ paq*frame + (1|id) + (1|vignette) ,family = "binomial", .)
summary(fit)
plot_model(fit, type = "int", terms="paq [all]")
```
> Marginally signifciant support


Secondary analyses
===

Frame x key issue
```{r}
fit <- df_framing_l %>% 
  mutate_at(vars(frame, vignette), as.factor) %>% 
  glm(choice ~ frame*keyIssue,family = "binomial", .)
summary(fit)
plot_model(fit, type = "int")
```
> The data are trending in the direction that if the vignette refers to what politicians see as a key issue, then the framing effect is bigger. However, this is not even close to significance. 

Frame x key issue (no dpecon)
```{r}
fit <- df_framing_l %>% 
  mutate_at(vars(frame, vignette), as.factor) %>% 
  filter(vignette != "dpecon") %>% 
  glm(choice ~ frame*keyIssue,family = "binomial", .)
summary(fit)
plot_model(fit, type = "int")
```
> Here I removed the dpecon vignettes since they are hard to interpret. Now it definitely seems like there is a larger framing effect if you see the vignette as pertaining to the key issue for Norway. This is super interesting because you could say that the people who care the most about an issue are the ones least equipped to make decisions about that issue.

Frame x vignette
```{r}
fit <- df_framing_l %>% 
  mutate_at(vars(frame, vignette), as.factor) %>% 
  glm(choice ~ frame*vignette,family = "binomial", .)
summary(fit)
plot_model(fit, type = "int")
```
> There is significantly less of a framing effect in conditions which involve data privacy than in conditions which involve jobs saved and lost. The econ condition looks similar to how the traditional Asian Disease Problem result from Kahneman and Tversky. I wonder whether people/politicians view a data privacy breach in terms of how many people's information was unsecured or whether people think of privacy breaches simply in terms of whether or not it occurred. This may be different than something like jobs lost where the quantity of jobs lost is more salient. Also, given the previous findings, it might mean that people care less about data breaches than jobs lost which is why you see less framing effect.

Frame x age
```{r}
fit <- df_framing_l %>% 
  left_join(df_inddiff) %>% 
  mutate_at(vars(frame, vignette), as.factor) %>% 
  glm(choice ~ frame*age, family = "binomial", .)
summary(fit)
plot_model(fit, type = "int")
```

Frame x gender
```{r}
fit <- df_framing_l %>% 
  left_join(df_inddiff) %>% 
  filter(gender == 0 | gender == 1) %>% 
  mutate_at(vars(frame, vignette), as.factor) %>% 
  glm(choice ~ frame*gender, family = "binomial", .)
summary(fit)
plot_model(fit, type = "int")
```
> Trending towards larger framing effect for women, but not significant.

PAQ interactions
---
Three way interaction: PAQ x Frame x Vignette
```{r}
df_framing_l %>% 
  left_join(df_inddiff) %>% 
  group_by(id, paq, frame, vignette) %>% 
  summarize(n = n()) %>% 
  arrange(desc(n))
fit <- df_framing_l %>% 
  mutate_at(vars(frame, vignette), as.factor) %>% 
  left_join(df_inddiff) %>% 
  glm(choice ~ paq*frame*vignette,family = "binomial", .)
summary(fit)
plot_model(fit, type = "int", terms="paq [all]")
```
> No three-way interaction.


```{r}
fit <- df_framing_l %>% 
  left_join(df_inddiff) %>% 
  mutate_at(vars(paq, age), scale) %>% 
  glmer(choice ~ paq*frame*age + (1|id) + (1|vignette) ,family = "binomial", .)
summary(fit)
plot_model(fit, type = "int", terms="paq [all]")
```
> no age moderation

```{r}
fit <- df_framing_l %>% 
  left_join(df_inddiff) %>% 
  mutate_at(vars(paq, age), scale) %>% 
  glmer(choice ~ paq*frame*gender + (1|id) + (1|vignette) ,family = "binomial", .)
summary(fit)
plot_model(fit, type = "int", terms="paq [all]")
```
> no gender three way moderation

Frame x key issue x PAQ (no dpecon)
```{r}
fit <- df_framing_l %>% 
  left_join(df_inddiff) %>% 
  filter(vignette != "dpecon") %>% 
  glm(choice ~ frame*keyIssue*paq,family = "binomial", .)
summary(fit)
plot_model(fit, type = "int")
```
> No three way interaction with whether it's a key issue. Frankly, there's just not enough power for this anyway.


Session Info
===
```{r}
sessionInfo()
```

